Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-04 article.tex
addeed results sub headings

    What are the factors of environmental sustainability in the Australian winegrowing industry?
        Purpose: Explore and understand the both the literature and industry perspectives on this.
        Results Literature review. Industry list of factors.

    How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
        Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
        Results: Use the agreed upon definitions to fully realise factors and their impact.

@@

    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
        Purpose: Examine regional differences and tailor sustainability strategies.
        Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

@@

    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are percieveed to directly impact environmental sustainability.
        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

>>>>

\subsection{Industry definitions}
How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
Results: Use the agreed upon definitions to fully realise factors and their impact.

\subsection{Comparative Analysis of Literature and Industry Perspectives}
    What are the factors of environmental sustainability in the Australian winegrowing industry?
        Purpose: Explore and understand the both the literature and industry perspectives on this.
        Results Literature review. Industry list of factors. Mind Map? Leximancer network.
        - Use the same words as the definitions in the search to show the parralels and differences.

@@

        \subsection{Sustainability in Coonawarra Winegrowing: Key Factors and Influences}
        Sustainability in Coonawarra Winegrowing: Key Factors and Influences
    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
        Purpose: Examine regional differences and tailor sustainability strategies.
        Results: Compare the generic model to the Coonawarra model. Acknowledge there is more work to be done here due to the amount of regions across Australia and the world. Prevous work also helps to illustrate these differences.

@@

\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are percieveed to directly impact environmental sustainability.
        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
